Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-15 paper/main.tex
\ac{foo}s -> \acp{foo}

The Tahoe-\ac{LAFS} is a distributed, secure file system perfectly suited to
build file sharing services over the Internet. Currently it uses the
\ac{SHA}-256 algorithm to verify the integrity of files and shares, in addition
to creating keys, \ac{URI}s and more \cite{t_tahoe}.

@@

\paragraph{Shavite3} seems to have received an update\footnote{See
\url{http://www.cs.technion.ac.il/~orrd/SHAvite-3/}}. We have observed that
implementations of Shavite3 in \ac{SUPERCOP}-20101014 or later seems to fail to
verify the \ac{KAT}s, while the version we have used does. We believe this is
only because newer \ac{KAT}s will have to be generated, but since the author
has not done so, we chose to use an older version of the algorithm.

@@

\paragraph{Incorrect implementations} are present in \ac{SUPERCOP}. By this we
mean implementations that does not conform to the \ac{KAT}s supplied or
implementations which fail completely as hash functions, see section
\ref{sec:choosen_implementations} for details on the JH implementation.

>>>>

The Tahoe-\ac{LAFS} is a distributed, secure file system perfectly suited to
build file sharing services over the Internet. Currently it uses the
\ac{SHA}-256 algorithm to verify the integrity of files and shares, in addition
to creating keys, \acp{URI} and more \cite{t_tahoe}.

@@

\paragraph{Shavite3} seems to have received an update\footnote{See
\url{http://www.cs.technion.ac.il/~orrd/SHAvite-3/}}. We have observed that
implementations of Shavite3 in \ac{SUPERCOP}-20101014 or later seems to fail to
verify the \acp{KAT}, while the version we have used does. We believe this is
only because newer \acp{KAT} will have to be generated, but since the author
has not done so, we chose to use an older version of the algorithm.

@@

\paragraph{Incorrect implementations} are present in \ac{SUPERCOP}. By this we
mean implementations that does not conform to the \acp{KAT} supplied or
implementations which fail completely as hash functions, see section
\ref{sec:choosen_implementations} for details on the JH implementation.
